---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AverageByGroup

<!-- badges: start -->
<!-- badges: end -->

The goal of AverageByGroup is to take in a dataset, and produce a tibble containing calculated averages of a numerical variable, grouped according to a categorical variable. This package is dependent on the tidyverse and dplyr packages. 

## Installation

You can install the development version of AverageByGroup like so:

``` r
# install.packages("devtools")
devtools::install_github("https://github.com/stat545ubc-2023/AverageByGroup.git", ref = "0.1.0")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(AverageByGroup)
#Here using the iris dataset, I will find the average of the petal width for each species
average_by_group(iris, Species, Petal.Width)
#the same can be done for a different dataset and different variables
average_by_group(PlantGrowth, group, weight)
```
